\Title

### 2021-01-27 manuscript/manuscript.tex

Window size:

In comparison with the non-boosted equivalent sources, we can see that the
gradient-boosted ones produce slightly less accurate results due to not being
able to achieve the global minimum of the least-squares problem, but they
perform faster.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows gets larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
When using gradient-boosted equivalent sources we can conclude that we want to
maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.

Overlap:

We can then conclude that using overlap values between 40\% and 70\% generate
a balance between predictions accuracy and computational time needed to fit the
source coefficients.
This corroborates that our naive choice of 50\% is good enough for producing
accurate predictions in reasonable times.

>>>>

From figures~\ref{fig:gradient-boosted-comparison}a
and~\ref{fig:gradient-boosted-comparison}c we can see that the gradient-boosted
equivalent sources produce slightly less accurate results by failing to achieve
the global minimum of the least-squares problem, but they perform faster than
the non-boosted ones.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows get larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
When using gradient-boosted equivalent sources we can conclude that is
desirable to maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.

From the results shown in Figures~\ref{fig:gradient-boosted-comparison}b
and~\ref{fig:gradient-boosted-comparison}d we can conclude that using
overlap values between 40\% and 70\% generate a balance between predictions
accuracy and computational time needed to fit the source coefficients.
This corroborates that our naive choice of 50\% is good enough for producing
accurate predictions in reasonable times.
